---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# FTreferateR

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

The goal of FTreferateR is to provide an R package that collects and parse minutes from the Danish Parliament.

## Installation

<!--You can install the released version of FTreferateR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("FTreferateR")
```-->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("emillykkejensen/FTreferateR")
```
## Example

This is a basic example which shows you how to get a list of all available parliamentary sessions, use that list to get a list of all meetings in that session and then get the data for all those meetings as a list of data.tables.

```{r example}
library(FTreferateR)

# Get a list of all available parliamentary sessions
FT_sessions <- getList_Session()

# Get a list of all meetings in that session
FT_meetings <- getList_Meeting(FT_sessions[3])

# Return the parsed meeting minutes as a list of data.tables
FT_data <- get_MeetingData(FT_meetings, verbose = TRUE)

```

### I need it all

The above code, only returns data for one session. If you wish to get all the available data run the code below - however note, that it will take some time ~2 hours.

```{r example_all_data, eval=FALSE, include=TRUE}
library(magrittr)

FT_data <- 
  getList_Session() %>%
  getList_Meeting() %>%
  get_MeetingData()

```

```{r example_get_data, include=FALSE}
load("~/all_FTdata.RData")
```


### Then go explore the data!

```{r ggplot2}
library(data.table)
library(ggplot2)

Aktivitet <- FT_data$Aktivitet

ggplot(Aktivitet[OratorRole == "medlem", 
                 .(.N), by = "TalerTitel"][order(-N)][1:20]) +
  geom_col(aes(x = reorder(TalerTitel, N), y = N)) +
  coord_flip() +
  theme_classic() +
  labs(x = NULL, y = "Antal gange man har taget ordet")


```

```{r ggplot22}

ggplot(Aktivitet[OratorRole == "medlem" & 
                   TaleType %like% "Ordfører",
                 .(.N), by = "TalerTitel"][order(-N)][1:20]) +
  geom_col(aes(x = reorder(TalerTitel, N), y = N)) +
  coord_flip() +
  theme_classic() +
  labs(x = NULL, y = "Antal gange man har holdt ordførertale")

```

